\begin{enumerate}
  \item R.~Aoshima, \underline{J.~Kurihara}, T.~Tanaka, ``Aggregable generalized deduplication,'' to Appear in \textit{IEICE Transactions on Communications}, 2026.
  \item K.~Nakano, \underline{J.~Kurihara} and T.~Tanaka, ``Extensive study on the security of private information delivery from coded storage,'' to Appear in \textit{IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences}, vol.~E109-A, no.~3, Mar. 2026.
  \item T.~Hasegawa, Y.~Koizumi, J.~Takemasa, \underline{J.~Kurihara}, T.~Tanaka, T.~Wood and K.~K.~Ramakrishnan, ``Leveraging Heterogeneous Programmable Data Planes for Security and Privacy of Cellular Networks, 5G \& Beyond,'' \textit{IEICE Transactions on Information and Systems}, vol.~E108-D, no.~6, pp.~485--493, Jun. 2025.
  \item I.~Kurihara, \underline{J.~Kurihara} and T.~Tanaka, ``A New Security Measure in Secret Sharing Schemes and Secure Network Coding,'' \textit{IEEE Access}, vol.~12, pp.~69163--69171, May 2024.
  \item \underline{J.~Kurihara}, T.~Kubo and T.~Tanaka, ``$\mu$ODNS: A Distributed Approach to DNS Anonymization with Collusion Resistance,'' \textit{Computer Networks}, Elsevier, vol.~237, p.~110078, Dec. 2023.
  \item \underline{J.~Kurihara}, T.~Nakamura and R.~Watanabe, ``Private information retrieval from coded storage in the presence of omniscient and limited-knowledge Byzantine adversaries'', \textit{IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences}, vol.~E104-A, no.~9, pp.~1271--1283, Sep. 2021.
  \item Y.~Koike, T.~Hayashi, \underline{J.~Kurihara} and T.~Isobe, ``Virtual Vault: A practical leakage resilient scheme using space-hard ciphers,'' \textit{IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences}, vol.~E104-A, no.~1, pp.~182--189, Jan. 2021.
  \item \underline{J.~Kurihara}, and T.~Nakamura, ``On the resistance to Byzantine and unresponsive servers in code-based PIR schemes,'' \textit{IEICE Communications Express}, vol.~9, no.~7, pp.~342--347, Jul.~2020.
  \item K.~Ueda, K.~Yokota, \underline{J.~Kurihara}, A.~Tagami, ``Two-level named packet forwarding for enhancing the performance of virtualized ICN router,'' \textit{IEICE Transactions on Communications}, vol.~E102-B, no.~2, pp.~1813--1821, Sep.~2019.
  \item \underline{J.~Kurihara}, K.~Yokota, and A.~Tagami, ``List interest: Simply packing interests dramatically reduces router workload in content-centric networking,'' \textit{IEICE Transactions on Communications}, vol.~E99-B, no.~12, pp.~2520--2531, Dec.~2016.
  \item \underline{J.~Kurihara}, R.~Matsumoto, and T.~Uyematsu, ``Relative generalized rank weight of linear codes and its applications to network coding'' \textit{IEEE Transactions on Information Theory}, vol.~61, no.~7, pp.~3912--3936, Jul. 2015.
  \item \underline{J.~Kurihara}, and Y.~Miyake, ``Securing distributed storage systems based on arbitrary regenerating codes,'' \textit{IEICE Communications Express}, vol.~2, no.~10, pp.442--446, Oct. 2013.
  \item \underline{J.~Kurihara}, T.~Uyematsu, and R.~Matsumoto,
    ``Secret sharing schemes based on linear codes can be precisely
    characterized by the relative generalized Hamming weight,''
    \textit{IEICE Transactions on Fundamentals of Electronics,
    Communications and Computer Sciences},
    vol.~E95-A, no.~11, pp.~2067--2075, Nov. 2012.
  \item Y.~Nakano, \underline{J.~Kurihara}, S.~Kiyomoto, and T.~Tanaka, ``Stream cipher-based hash function and its security,'' \textit{Revised Selected Papers in the 7th International Joint Conference e-Business and Telecommunications, ICETE 2010, Athens, Greece, July 26--28, 2010}, ser.~Communications in Computer and Information Science, vol.~222, \hskip 1em plus 0.5em minus 0.4em\relax Heidelberg, Germany: Springer-Verlag, pp.~188--202, 2012.
  \item \underline{J.~Kurihara}, and T.~Uyematsu, ``A novel realization
    of threshold schemes over binary field extensions,''
    \textit{IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences},
    vol.~E94-A, no.~6, pp.~1375--1380, Jun. 2011.
  \item \underline{J.~Kurihara}, S.~Kiyomoto, R.~Watanabe, and
    T.~Tanaka, ``A stream authentication method for one-seg
    broadcasting,'' \textit{Journal of the Institute of Image
    Information and Television Engineers},
    vol.~64, no.~12, pp.~1921--1932, Dec. 2010. (in Japanese)
  \item \underline{J.~Kurihara}, S.~Kiyomoto, K.~Fukushima, and
    T.~Tanaka, ``A fast $(k,L,n)$-threshold ramp secret sharing
    scheme,'' \textit{IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences},
    vol.~E92-A, no.~8, pp.~1808--1821, Aug. 2009.
  \item \underline{J.~Kurihara}, S.~Kiyomoto, K.~Fukushima, and
    T.~Tanaka, ``On a fast $(k,n)$-threshold secret sharing scheme,''
    \textit{IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences},
    vol.~E91-A, no.~9, pp.~2365--2378, Sep. 2008.
  \item \underline{J.~Kurihara}, S.~Kiyomoto, K.~Fukushima, and
    T.~Tanaka, ``A fast $(3,n)$-threshold secret sharing scheme using
    exclusive-or operations,''
    \textit{IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences},
    vol.~E91-A, no.~1, pp.~127--138, Jan. 2008.
  \item A.~Deininger, S~ Kiyomoto, \underline{J.~Kurihara}, and
    T.~Tanaka, ``Security vulnerabilities and solutions in mobile
    WiMAX,'' \textit{IJCSNS International Journal of Computer Science
    and Network Security}, vol.~7, no.~11, pp.~7--15, Nov. 2007.
\end{enumerate}
